Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-05-03 hotstorage13/background.tex
correction

%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided. 
%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
%only a very small slice of cluster resource can be used for the backup purpose.

@@

This paper considers a backup service uses the existing cluster computing resource. 
Another option is to attach  a separate backup system with deduplication
support the cluster, and  every machine can periodically transfer snapshots to
the attached backup system.
%One  weakness of this approach is communication bottleneck between a large number of machines
%in a cloud to this centralized  service.
The cost of allocating the above dedicated backup  resource can be expensive.
Since most of backup data is not used eventually, CPU and memory resource in such a backup service may 
not be fully utilized. This paper seeks for on a low-cost architecture option.

%It should be emphasized that our approach does not  accumulate raw backup data temporarily for deduplication
%and does not require a significant amount of extra storage capacity.
%Our strategy is to perform a drity  scan to collect
% a small amount of disk space  to accumulate
%deduplicate requests along with necessary meta data, and perform actual backup after deduplicate detection completes.

>>>>

%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided. 
%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
%only a very small slice of cluster resource can be used for the backup purpose.

@@

\comments{
This paper considers a backup service uses the existing cluster computing resource. 
Another option is to attach  a separate backup system with deduplication
support the cluster, and  every machine can periodically transfer snapshots to
the attached backup system.
%One  weakness of this approach is communication bottleneck between a large number of machines
%in a cloud to this centralized  service.
The cost of allocating the above dedicated backup  resource can be expensive.
Since most of backup data is not used eventually, CPU and memory resource in such a backup service may 
not be fully utilized. This paper seeks for a low-cost architecture option.
}
%It should be emphasized that our approach does not  accumulate raw backup data temporarily for deduplication
%and does not require a significant amount of extra storage capacity.
%Our strategy is to perform a drity  scan to collect
% a small amount of disk space  to accumulate
%deduplicate requests along with necessary meta data, and perform actual backup after deduplicate detection completes.
